---
title: |
  | Supplementary Information for: 
  | "Modeling the effects of crime type and evidence on judgments about guilt"
author: "Pearson et al."
date: "9/28/2018"
output:
  pdf_document:
    fig_caption: yes
    keep_tex: false
  html_document: default
header-includes:
- \usepackage{amsmath, amssymb}
- \usepackage[labelfont=bf]{caption}
- \usepackage{float}

bibliography: supp.bib
---
\captionsetup[table]{name=Supplementary Table}
\captionsetup[figure]{name=Supplementary Figure}

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.pos= "H", out.extra='')
```
# Supplementary Methods

## Scenario crime descriptions and evidence options

```{r message=FALSE, echo=FALSE, warning=FALSE, results = "asis"}
library(jsonlite)

sc <- fromJSON('../data/scenarios.json', flatten=TRUE) 

template <- "### Scenario %s:
%s

- **Criminal History**
  - *Related*:   %s
  - *Unrelated*: %s
  - *No prior*:  %s

- **Witness**
  - *Witness*:   %s
  - *No witness*: %s

- **Physical evidence**
  - *DNA*:   %s
  - *non-DNA*: %s
  - *none*:  %s

"

sc_formatted <- sprintf(template, sc$abbr, 
                        sc[['vars.base.Base']],
                        sc[['vars.Criminal History.relatedPrior']],
                        sc[['vars.Criminal History.unrelatedPrior']],
                        sc[['vars.Criminal History.noPrior']],
                        sc[['vars.Witness.isWitness']],
                        sc[['vars.Witness.noWitness']],
                        sc[['vars.Physical Evidence.DNA']],
                        sc[['vars.Physical Evidence.nonDNA']],
                        sc[['vars.Physical Evidence.noPhys']]
                        )

cat(sc_formatted, sep='')
```

## Task Directions and Questions

### Standard directions

You are about to read a series of short, fictitious criminal cases. After
reading the accusation against the defendant, view additional
information by clicking each of the three grey buttons and holding for
as long as you want to read.

For example, clicking on the button labeled \"Physical Evidence\" would
show any physical evidence that had been found in the case. You may
click and read the facts in each box as many times as you like.

After reading the entire story and the additional information, reflect
on how you feel about the facts in the case as it is presented. Please
do not be concerned about making a legal judgment, especially with
regard to the rules of evidence or the law, but rather merely consider
your personal opinions and intuitions about the case. 

You will then be asked about the strength of the case against the
accused and the amount of punishment that type of crime deserves.

For each question, move the slider to the position that best reflects
your personal judgment.

When you are finished, click the Submit button to go to the next
question.

### Explicit/curative directions

You are about to read a series of short descriptions of fictitious
criminal cases. After reading the accusation against the defendant, view
additional information by clicking and holding down the mouse button
over each of the four grey boxes.

For example, clicking on the button labeled \"Physical Evidence\" would
show any physical evidence that had been found in the case. You may
click and read the facts in each box as many times as you like.

After reading the entire story, reflect on how you feel about the facts
in the case as it is presented. Do not be concerned about making a legal
judgment. Rather, think about your personal opinions and intuitions
about the case.

You will then be asked two questions.

First, how strong is the case against the person who was accused of the
crime? How confident are you, based on the evidence that you read, that
the accused actually did it? Is the evidence in the case strong or weak?
Do not let your feelings about the seriousness or awfulness of the crime
sway your judgment about whether that person actually committed the
crime.

The second question is the opposite. Setting aside whether you think the
accused committed the crime, how severely should anyone who commits a
crime like this be punished? Is it a horrible and heinous crime,
deserving of life in prison without parole? Or is it not serious, and
should be punished very lightly, if at all? When choosing the amount of
punishment, think only about the kind of crime that the accused is
accused of, not whether he or she actually did it.

For both questions, move the slider to the position that best reflects
your personal judgment. When you are finished, click the Submit button
to go to the next question.

### Questions

**Confidence** (C): How strong is the case that the accused committed this
crime?

Slider: Very weak, Very strong

**Punishment** (P): How severe should the punishment be for someone who
commits a crime like this one?

Slider: No punishment, Life in prison without parole

**Guilt** (G): Based on what you've read, do you think the accused is
guilty?

Button: Yes, guilty; No, not guilty

**Outrage** (O): When you read about crimes like this one, how upset to you
feel?

Slider: Not upset, Outraged

**Threat** (T): When you read about a crime like this, how concerned do you
fell for your own safety, or the safety of your community?

Slider: Not concerned at all, Very concerned

**Likelihood** (L): How likely is this crime to occur in your community?

Slider: Not at all likely, Very likely

## Single Rating Model
For the case of a single rating outcome (case strength), we separately model each group of participants as follows: Given a set of
ratings $R$ indexed by $i=1\ldots N$, and an $N \times P$ design matrix $X$ (with columns corresponding to regressors $p=1\ldots P$), we assume for a given observation $i$ corresponding to 
subject $s$ and case $c$:

\begin{align}
  R_i &\sim \left[\mathcal{N}(\theta_i, \sigma^2)\right]^{100}_0 \label{rating}\\
  \theta_i &= X_{i \,\cdot} \cdot \beta_{s(i) c(i) \,\cdot} \label{theta}\\
  \beta_{s c p} &\sim \mathcal{T}_{\nu}(\gamma_{c p}, \tau^2_{c p}) \label{beta}\\
  \gamma_{c p} &\sim \mathcal{T}_{\nu'}(\mu_p, \eta^2_p) \label{gamma}\\
  \mu_p &\sim \mathcal{N}(50, 50) \label{mu} \\
  \eta_p &\sim \mathrm{Ca}^+(0, 50) \\
  \tau_{c p} &\sim \mathrm{Ca}^+(0, 50) \\
  \sigma &\sim \mathrm{Ca}^+(0, 5) \\
  \nu, \nu' &\sim \mathcal{N}^+(0, 100) \label{nu}
\end{align}

That is:

- ratings are generated from a normal distribution censored to lie in the range $[0, 100]$ (\ref{rating})
- linear predictors of ratings are weighted sums of subject-, case-, and regressor-specific effects (\ref{theta})
- $\beta$ effects for each subject are drawn from a case- and regressor-specific distribution (\ref{beta})
- $\gamma$ effects for each case are themselves drawn from a regressor-specific distribution of effects (\ref{gamma})
- effects at the case and single-subject level are modeled as robuts/fat-tailed, with Student-t distributions (\ref{beta},\ref{gamma})
- variances ($\eta^2$, $\tau^2$, $\sigma^2$) are modeled using weakly informative half-Cauchy priors [@gelman2006prior], 
  while degrees of freedom ($\nu$, $\nu'$) are modeled using weak half-Normal priors

This approach allows for flexible fitting (including estimates of variance) at the regressor, case, and individual levels, while
at the same time leveraging partial pooling to share statistical strength across these levels [@gelman2006data].

## Multiple Rating Model
For the case in which subjects provide multiple ratings (punishment, case strength, etc.) for a given scenario, we model the resulting
vector of ratings, $R_r$, $r=1\ldots N_r$, similarly:

\begin{align}
  R_i &\sim \left[\mathcal{N}(\theta_i, \sigma^2_{r(i)})\right]^{100}_0 \label{rating_m}\\
  \theta_i &= X_{i \,\cdot} \cdot \beta_{s(i) c(i) \,\cdot \,r(i)} \label{theta_m}\\
  \beta_{s c p r} &\sim \mathcal{T}_{\nu}(\gamma_{c p r}, \tau^2_{p r}) \label{beta_m}\\
  \gamma_{c p} &\sim \mathcal{T}_{\nu'}(\mu_p, \Sigma_p) \label{gamma_m}\\
  \Sigma_p &= L_p \cdot \mathrm{diag}(\eta_p)\cdot L_p^\top \\
  \Omega_p = L_p L_p^\top &\sim \mathrm{LKJ}(1) \label{L_m}\\
  \mu_{p r} &\sim \mathcal{N}(50, 50) \label{mu_m} \\
  \eta_{p r} &\sim \mathrm{Ca}^+(0, 50) \\
  \tau_{p r} &\sim \mathrm{Ca}^+(0, 50) \\
  \sigma_r &\sim \mathrm{Ca}^+(0, 5) \\
  \nu, \nu' &\sim \mathcal{N}^+(0, 100) \label{nu_m}
\end{align}

Here, we have used a "long" or "melted" representation of $R$ in which each index $i$ corresponds to a single observation of a
single rating scale $r(i)$. This allows us to more easily handle missing data in the model fitting procedure (see below). 
The model is almost equivalent to concatenating $N_r$ versions of the first model, one for each rating, 
aside from two key differences: First (\ref{gamma_m}) and (\ref{L_m}) involve a multivariate t-distribution on the population 
effects specific to 
each case ($\gamma$). That is, we allow for covariance among the ratings for each effect at the population level, where the magnitudes of the 
variances are again controlled by $\eta$ and the correlations $\Omega = LL^\top$ are modeled according to the LKJ distribution [@Lewandowski2009-tm]
through their Cholesky factorization (\ref{L_m}).\footnote{Implemented as \texttt{L \textasciitilde{} lkj\_corr\_chol(1)} in Stan.}
Second, in order to more accurately estimate variances in the presence of missing data, we have restricted this model to a single
value of $\tau$ across all cases (for each outcome and regressor) (\ref{beta_m}).

## Model Fitting
We calculated posterior distributions and credible intervals for each variable of interest using Markov Chain Monte Carlo methods
as implemented in the Stan probabilistic programming language [@carpenter2016stan]. Full code for all analyses is available at 
[https://github.com/pearsonlab/legal](https://github.com/pearsonlab/legal). Models were fit by running 4 chains of either 1000 samples (case strength only model) with a thinning fraction of 1 or 2000
samples (multiple outcome models) with a thinning fraction of 2. For both models, the first half of samples were discarded as burn-in. This resulted 
in 2000 total samples for each variable, for which we report means as well as 95% equal-tailed credible intervals (bounded 
by the 2.5% and 97.5% samples from the distribution). We assessed convergence via effective sample size and the
Gelman-Rubin statistic, for which all runs had $\hat{R} < 1.1$ [@gelman2014bayesian]. We include plots of $\hat{R}$ for our our single-outcome, two-outcome, and all-outcome models in Supplementary Figures \ref{sv_rhat}, \ref{2v_rhat}, and \ref{mv_rhat}.

## Sensitivity Analysis
Given the large number of model parameters in comparison to the numer of data points, it is quite possible that our particular modeling assumptions might affect posterior inferences. To test this, we performed a sensitivity analysis in which the distributions for case- and subject-specific effects (\ref{beta}), (\ref{gamma}), (\ref{beta_m}), and (\ref{gamma_m}) were changed from Student t to normal. This assumption reflects a belief that few cases and subjects are true outliers, and should result in larger estimates of the relevant variance parameters and more shrinkage of estimates toward the mean. We re-ran all models (single-, double-, and multi-outcome) from our main analyses again using these alternate assumptions.

We found nearly identical results for the two models. Figures 2-4 from the main text are reproduced below as Supplementary Figures \ref{fig_2_norm}--\ref{fig_4_norm}. Indeed, in our single-response models, we verified posterior means $\mathbb{E}\nu > 100$ and $91 > \mathbb{E}\nu' > 61$ for all groups, indicating that our Student t models are very close to normal.

\newpage

# Supplementary Tables

## Demographics
Here, we give a breakdown of our mTurk sample. We include all participants, including those in Experiment 1C (no evidence), though these were not used in our models.
```{r message=FALSE, echo=FALSE, warning=FALSE, fig.height=6, fig.cap="\\label{demo_table}"}
library(tidyverse)
library(kableExtra)

mturk_demos <- read.csv('../data/combined_data.csv') %>% filter(group=='mturk') %>%
  distinct(uid, .keep_all=TRUE)

# renaming, etc.
cutpts = c(17, 21, 25, 30, 40, 50, 60, 90) # cutpoints for age ranges
mturk_demos$age = cut(mturk_demos$age,cutpts)

mturk_demos$gender <- factor(mturk_demos$gender, levels=c("Male", "Female", "Other"))
mturk_demos$race <- factor(mturk_demos$race, 
                           levels=c("American Indian or Alaska Native", 
                                    "Asian", 
                                    "Black or African American",
                                    "Native Hawaiian or other Pacific Islander",
                                    "White",
                                    "More than one race",
                                    "Unknown or do not want to disclose"))
mturk_demos$ethnicity <- factor(mturk_demos$ethnicity,
                                levels=c("Hispanic or Latino", 
                                         "Not Hispanic or Latino", 
                                         "Unknown or do not want to disclose"))
mturk_demos$education <- factor(mturk_demos$education,
                                levels=c("Less than high school", 
                                         "Completed high school",
                                         "GED", 
                                         "Some college",
                                         "Associate's Degree", 
                                         "Bachelor's Degree", 
                                         "Master's Degree", 
                                         "Ph.D.", 
                                         "Law degree",
                                         "Other professional degree"))
mturk_demos$political_party <- factor(mturk_demos$political_party, 
                                      levels=c("Independent or no party Affiliation", 
                                               "Republican", 
                                               "Democrat", 
                                               "Other", 
                                               "I am not a registered voter"))

get_count_tbl <- function(varname){
  id <- "uid"
  Ntot <- dim(mturk_demos)[1]
  tbl <- mturk_demos %>% select_(id, varname) %>% group_by_(varname) %>% 
    summarize(count=n(), percent=round(100 * n()/Ntot, 1))
  names(tbl) <- str_replace_all(names(tbl), "_", " ") %>% tools::toTitleCase()
  return(tbl)
}

kable(get_count_tbl("gender"), caption="Participant Demographics - Gender") %>%
  kable_styling(latex_options = c("HOLD_position"))
kable(get_count_tbl("age"), caption="Participant Demographics - Age") %>%
  kable_styling(latex_options = c("HOLD_position"))
kable(get_count_tbl("race"), caption="Participant Demographics - Race") %>%
  kable_styling(latex_options = c("HOLD_position"))
kable(get_count_tbl("ethnicity"), caption="Participant Demographics - Ethnicity") %>%
  kable_styling(latex_options = c("HOLD_position"))
kable(get_count_tbl("education"), caption="Participant Demographics - Education") %>%
  kable_styling(latex_options = c("HOLD_position"))
kable(get_count_tbl("political_party"), caption="Participant Demographics - Political Party") %>%
  kable_styling(latex_options = c("HOLD_position"))
```

## Experimental design
```{r message=FALSE, echo=FALSE, warning=FALSE}
library(tidyverse)
library(kableExtra)

dat <- read.csv('../data/combined_data.csv') %>% 
  select(uid, experiment, rating_type, rating) %>%
  na.omit %>%
  select(-rating) %>%
  distinct() %>%
  mutate(rating_type=factor(rating_type, levels=c(
    'rating', 'rate_punishment', 'rate_outrage', 'rate_threat', 'rate_threat_2', 'guilty'),
    labels=c('Confidence', 'Punishment', 'Outrage', 'Likelihood', 'Threat', 'Guilt')
  )) %>%
  rename(Experiment=experiment)


experiment_counts <- dat %>% select(-rating_type) %>% distinct() %>% 
  count(Experiment) %>% rename(Subjects=n)
question_counts <- dat %>% count(Experiment, rating_type) %>%
  spread(key=rating_type, value=n)
details_table <- data.frame(Experiment=c('1A', '1B', '1C', '1D', '1E', '1F', '2A', '2B', '2C'),
                            Description=c('Five questions',
                                          'Single question',
                                          'No evidence',
                                          'Explicit directions',
                                          'Two questions',
                                          'Threat',
                                          'Law students',
                                          'LA state bar',
                                          'IL prosecutors'),
                            Format=c('Group', rep('Sequential', 2), rep('Group', 6)))
subject_counts <- merge(details_table, merge(experiment_counts, question_counts))

op <- options(knitr.kable.NA = '')

kable(subject_counts, format="latex", booktabs=T, escape=F,
      caption="Task variations and subjects. Numbers in each column are numbers of subjects who answered each question for each experiment.\\label{exp_variants_table}",
      linesep=c('', '', '', '', '', '\\addlinespace')) %>% 
  kable_styling(full_width=F, latex_options = c("HOLD_position", "striped", "scale_down")) %>%
  add_header_above(c(" " = 4, "Question" = 6))

options(op)
```

```{r message=FALSE, echo=FALSE, warning=FALSE}
library(tidyverse)
library(kableExtra)

analysis_sets <- data.frame(Figure=c('1', '1', '1', '2', '3', '4', '4'),
                            Panels=c('B', 'C', 'D', 'A, B, C', 'A, B, C, D', 'A, B, C', 'D'),
                            Criteria=c('mTurk, evidence presented, confidence question',
                                       'mTurk, evidence presented, confidence \\emph{and} guilt questions',
                                       'mTurk, evidence presented, punishment question',
                                       'mTurk, evidence presented, confidence question',
                                       'evidence presented, confidence question',
                                       'mTurk, evidence presented, any non-guilt question',
                                       'evidence presented, \\emph{either} confidence or punishment question'),
                            Experiments=c('1A, 1B, 1D, 1E, 1F',
                                          '1A',
                                          '1A, 1B, 1D, 1E',
                                          '1A, 1B, 1D, 1E, 1F',
                                          '1A, 1B, 1D, 1E, 1F, 2A, 2B, 2C',
                                          '1A, 1B, 1D, 1E, 1F',
                                          '1A, 1B, 1D, 1E, 2A, 2B, 2C'))

kable(analysis_sets, format="latex", booktabs=T, escape=F,
      caption="Subsets of data used in each analysis.\\label{subsets_table}") %>% 
  kable_styling(full_width=F, latex_options = c("HOLD_position", "striped", "scale_down"))
```

```{r message=FALSE, echo=FALSE, warning=FALSE}
library(tidyverse)
library(kableExtra)

sc_class <- read.csv('../data/scenario_classification.csv', check.names=FALSE) %>%
  select(`Scenario`, `Base crime description`, `Crime type`, `Category`, `Class`) 

kable(sc_class, format="latex", booktabs=T, escape=T, longtable=T,
      caption="Scenario legal classifications.\\label{seriousness_table}")  %>%
  column_spec(2, width='20em') %>%
  column_spec(c(3, 5), width='8em') %>%
  kable_styling(full_width=F, latex_options = c("HOLD_position", "striped", "repeat_header"))
```

## Posteriors for differences in evidence effects
In Tables \ref{group_effects_table} and \ref{outcome_effects_table}, we give 95\% credible intervals for the posterior differences in mean evidence effects across our population samples (Table \ref{group_effects_table}; cf. Figure 3A) and different rating types (Table \ref{outcome_effects_table}; cf. Figure 4A). That is, for each pair of variables, the numbers represent an interval that contains 95\% of the posterior probability mass.

```{r message=FALSE, echo=FALSE, warning=FALSE}

load('../data/stan_postprocess_ci.rdata')
not_in_ci <- function(ci, x=0) {
  ifelse(x >= ci[[1]] && x <= ci[[2]], F, T)
}
ci_table <- group_ci_df %>% 
  mutate_all(funs(lapply(., function(x){lapply(x, round, 1)}))) %>%
  mutate_all(funs(cell_spec(., "latex", bold=lapply(., not_in_ci)))) %>%
  mutate_all(funs(str_replace(., "list", "")))
row.names(ci_table) <- row.names(group_ci_df)

kable(ci_table, format="latex", booktabs=T, escape=F,
      caption="Bayesian 95\\% equal-tailed credible intervals for contrasts 
      between population mean effects. Cf. Figure 3A in main text. Intervals excluding 0 are in bold.\\label{group_effects_table}") %>% 
  kable_styling(full_width=F, latex_options = c("HOLD_position"), font_size=8) %>%
  column_spec(1, width = "10em") %>%
  column_spec(2:7, width = "6.5em")


ci_table <- ratings_ci_df %>% 
  mutate_all(funs(lapply(., function(x){lapply(x, round, 1)}))) %>%
  mutate_all(funs(cell_spec(., "latex", bold=lapply(., not_in_ci)))) %>%
  mutate_all(funs(str_replace(., "list", "")))
row.names(ci_table) <- row.names(ratings_ci_df)

kable(ci_table, format="latex", booktabs=T, escape=F,
      caption="Bayesian 95\\% equal-tailed credible intervals for contrasts 
      between rating type mean effects. Cf. Figure 4A in main text. Intervals excluding 0 are in bold.\\label{outcome_effects_table}") %>% 
  kable_styling(full_width=F, latex_options = c("HOLD_position"), font_size=8) %>%
  column_spec(1, width = "10em") %>%
  column_spec(2:7, width = "6.5em")
```

\newpage

# Supplementary Figures


```{r message=FALSE, echo=FALSE, warning=FALSE, fig.height=4, fig.cap="Absence of task learning effect. Comparison of distributions of first and last five ratings given by each participant. \\label{task_learning_effect}"}
source("../ggplot_setup.R")

mturk_ratings <- read.csv('../data/combined_data.csv') %>% 
  filter(group=='mturk', evidence_shown, rating_type != 'guilty')
maxq <- max(unique(mturk_ratings$question))

# filter to first five and last five questions 
first_last <- mturk_ratings %>% filter(question < 5 | maxq - question < 5) %>% 
  mutate(early = factor(question < 5, levels=c(TRUE, FALSE), labels=c("Early", "Late")))

# Density plot early vs late ratings
plt <- ggplot(first_last) +
  geom_density(aes(x=rating, fill=early), alpha=0.5) +
  xlab("Confidence in Guilt") +
  ylab("Density") +
  scale_fill_discrete(name = "Scenario occurrence") +
  th +
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        legend.title=element_text(),
        legend.position=c(0.15, 0.9))
plot(plt)
```

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.height=6, fig.cap="Deserved punishment ratings as a function of crime severity. Plotted separately for State (A) and Federal (B) crimes. \\label{seriousness_by_crime_type}"}
library(tidyverse)
library(grid)
library(gridExtra)
source("../ggplot_setup.R")

load('../data/stan_postprocess_2v_t.rdata')

# dataframe linking scenarios to seriousness as rank ordered by PS
sc_ranked <- as.factor(c(27, 6, 12, 29, 13, 14, 1, 24, 2, 22, 25,
                                        3, 8, 9, 4, 18, 33, 15, 7, 19, 28, 32, 5, 11, 26, 17,
                                        20, 30, 31, 21, 10, 16, 23))
crime_type <- rep('state', 33)
crime_type[c(1, 14, 28)] <- 'federal'
crime_type <- as.factor(crime_type)

seriousness <- data.frame(seriousness=as.factor(c(1:33)), 
                          scenario=sc_ranked,
                          crime_type=crime_type)

df <- merge(dat, seriousness) %>% filter(rating_type=='rate_punishment') %>% 
  group_by(scenario, seriousness, crime_type) %>% 
  summarise(punish=median(rating), lower=quantile(rating, 0.25), 
            upper=quantile(rating, 0.75))
  

# boxplot punishment rating by seriousness
plt_1 <- ggplot(df %>% filter(crime_type=='state')) +
  geom_pointrange(aes(seriousness, punish, ymin=lower, ymax=upper), color=color_conf) + 
  # geom_smooth(aes(as.numeric(seriousness), punish), color=color_conf, span=0.85, fullrange=TRUE) +
  scale_x_discrete(name='Scenario (rank-ordered by severity)',
                   breaks=c(1:33),
                   labels=seriousness$scenario) + 
  coord_cartesian(ylim=c(0, 100)) +
  labs(title="A. State Crimes", size=rel(3)) +
  ylab("Punishment Rating (points)") +
  th +
  theme(
    axis.text.x = element_text(size=rel(0.75))
    )

plt_2 <- ggplot(df %>% filter(crime_type=='federal')) +
  geom_pointrange(aes(seriousness, punish, ymin=lower, ymax=upper), color=color_conf) + 
  # geom_smooth(aes(as.numeric(seriousness), punish), color=color_conf, span=0.85, fullrange=TRUE) +
  scale_x_discrete(name='Scenario (rank-ordered by severity)',
                   breaks=c(1:33),
                   labels=seriousness$scenario) + 
  coord_cartesian(ylim=c(0, 100)) +
  labs(title="B. Federal Crimes", size=rel(3)) +
  ylab("Punishment Rating (points)") +
  th +
  theme(
    axis.text.x = element_text(size=rel(0.75))
    )
plot(arrangeGrob(plt_1, plt_2))
```

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width=8, fig.cap="Comparison of evidence and demographic effects for the mTurk sample (cf. Figure 2A). Analyses were performed on a reduced sample of $N=368$ participants with complete demographic information for the variables displayed.  Demographic variables were modeled as additional $\\beta$ effects as in (\\ref{theta}) and (\\ref{beta}). \\label{demo_effects}"}

# based on postprocess_stan_hier_data.R and make_paper_figure_2.R
library(tidyverse)
library(ggplot2)

load('../data/stan_postprocess_demos_t.rdata')

fe <- effects %>% filter(variable == 'mu', evidence != 'baseline') %>%
      select(mean, evidence, X2.5., X97.5.) %>%
      mutate(evidence=factor(evidence, levels=c("physicalDNA", 
                                                "physicalNon-DNA", 
                                                "witnessYes Witness", 
                                                "historyRelated", 
                                                "historyUnrelated",
                                                "femaleTRUE",
                                                "nonwhiteTRUE",
                                                "hispanicTRUE")))

effects_x_axis <- scale_x_discrete(breaks=c("physicalDNA", 
                                             "physicalNon-DNA", 
                                             "witnessYes Witness", 
                                             "historyRelated", 
                                             "historyUnrelated",
                                             "femaleTRUE",
                                             "nonwhiteTRUE",
                                             "hispanicTRUE"), 
                                     labels=c("DNA \nphysical \nevidence", 
                                              "Non-DNA \nphysical \nevidence",  
                                              "Witness \npresent", 
                                              "Related \nprior crime", 
                                              "Unrelated \nprior crime",
                                              "Female -\nMale",
                                              "Non-white -\nWhite",
                                              "Hispanic -\nNon-hispanic"))
plt_1 <- ggplot(data=fe) +
  geom_pointrange(aes(x=evidence, y=mean, ymin=X2.5., ymax=X97.5.), color=color_conf, size=1.) + 
  effects_x_axis +
  coord_cartesian(ylim=c(-10,40)) +
  ylab("Confidence in Guilt (points)") +
  xlab("Effects") +
  geom_vline(xintercept=1.5, colour='grey') +
  geom_vline(xintercept=2.5, colour='grey') +
  geom_vline(xintercept=3.5, colour='grey') +
  geom_vline(xintercept=4.5, colour='grey') +
  geom_hline(yintercept=0.0, colour='grey') + 
  th +
  theme(
    axis.text.x = element_text(hjust = 0.5, size=rel(1), color='black'))
plt_1
```

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width=8, fig.cap="Comparison of sources of model variance. Points indicate posterior means of variance parameters. Lines indicate 95\\% credible intervals. Boxplots indicate variability of variance parameters across scenarios. Columns correspond to model variance parameters $\\tau^2$, $\\eta^2$, and $\\sigma^2$, respectively. \\label{model_variance_comparison}"}

load('../data/stan_postprocess_sv_t.rdata')

variance_comparison <- effects %>%
  filter(variable %in% c('eta', 'tau', 'sigma'), (evidence=='baseline') | (variable == 'sigma')) %>%
  select(X2.5., X50., X97.5., variable, scenario, group) %>%
  mutate(variable = factor(variable, levels=c('eta', 'tau', 'sigma')))

plt_5 <- ggplot() +
  geom_pointrange(data=variance_comparison %>% filter(variable %in% c('eta', 'sigma')),
                  aes(x=variable, y=X50., ymin=X2.5., ymax=X97.5., color=group),
                  position=position_dodge(width=0.5), size=1) +
  geom_boxplot(data=variance_comparison %>% filter(variable=='tau'),
               aes(x=variable, y=X50., color=group), lwd=1, fatten=1, 
               position=position_dodge(width=0.85)) +
  variance_x_axis +
  group_color_scale +
  ylim(0, 50) +
  ylab("Standard Deviation (points)") + 
  xlab("Variance") +
  th +
  theme(
    axis.text.x = element_text(hjust = 0.5, size=rel(1), color='black'),
    legend.position = c(0.8, 0.8)
  )
plt_5
```

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width=8, fig.cap="Pairwise correlations for baseline effects across all outcome types. Includes in addition data for the likelihood question (cp. Figure 4C). \\label{baseline_correlations}"}
load('../data/stan_postprocess_mv_t.rdata')

outcomes <- levels(effects$outcome)
Nr <- length(outcomes)
releveler <- function(x) {
  # replace outcome numbers with names
  xfac <- factor(x, levels=1:length(outcomes), labels=outcomes)
  
  # now reorder levels so plot looks right
  factor(as.character(xfac), levels=c("rating", "rate_punishment", "rate_outrage", "rate_threat", "rate_threat_2", "guilty"))
}
corrs <- effects %>% filter(grepl('Omega', variable)) %>% 
                     separate(variable, into=c("variable", "outcome1", "outcome2")) %>%
                     mutate_at(c("outcome1", "outcome2"), releveler) %>%
                     filter(outcome1 != 'guilty', outcome2 != 'guilty') %>%
                     filter(evidence=='baseline') %>% 
                     unite(col=contrast, outcome1, outcome2, sep='-') %>%
                     mutate(contrast=factor(contrast, levels=outcome_corr_levels,
                                                      labels=outcome_corr_labels))

plt_3 <- ggplot(data = corrs) +
  geom_hline(yintercept=0, colour='grey') +
  geom_pointrange(aes(x=contrast, y=X50., ymin=X2.5., ymax=X97.5.)) + 
  ylab('Baseline Correlation') +
  xlab('Outcome Pair') +
  coord_cartesian(ylim=c(-1,1)) +
  th +
  theme(
    axis.text.x = element_text(hjust = 0.5, size=rel(0.8), color='black')
  )
plt_3  
```

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width=8, fig.cap="Correlations between case strength and deserved punishment for all model effects across groups (cp. Figure 4D). \\label{all_group_correlations}"}

load('../data/stan_postprocess_2v_t.rdata')

plt_4 <- ggplot(data=(effects %>% filter(grepl('Omega', variable)))) +
  geom_hline(yintercept=0, colour='grey') +
  geom_pointrange(aes(x=evidence, y=X50., ymin=X2.5., ymax=X97.5., color=group), 
                         position=position_dodge(width = 0.5)) + 
  xlab('Evidence') + ylab('\nConfidence in Guilt /\nPunishment Correlation') +
  group_color_scale +
  evidence_plus_baseline_x_axis +
  th + 
  theme(
    axis.text.x = element_text(hjust = 0.5, size=rel(1), color='black'),
    legend.position=c(0.15, 0.2),
    legend.box.background = element_rect(fill=alpha("white", 0.75), color=NULL, linetype=NULL)
  )
plt_4
```


```{r message=FALSE, echo=FALSE, warning=FALSE, fig.height=4, fig.width = 8, fig.cap="Convergence diagnostic for MCMC fitting procedure for the single outcome model. Box plots show Gelman-Rubin statistics ($\\hat{R}$) for each of the variables in the model. Color indicates sample groups, which were fit using separate models. Values $\\hat{R} < 1.1$ are typically taken to represent satisfactory convergence. For variable definitions, see (\\ref{rating}) - (\\ref{nu}). \\label{sv_rhat}"}
library(tidyverse)
library(kableExtra)

load('../data/stan_postprocess_sv_t.rdata')

plt <- ggplot(effects) + 
  geom_boxplot(aes(y=Rhat, x=variable, color=group)) +
  group_color_scale +
  labs(title="Convergence diagnostics:\nSingle response model", size=rel(3)) +
  th + 
  theme(legend.position=c(0.68, 0.75))
plt
```

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.height=4, fig.width = 8, fig.cap="Convergence diagnostic for MCMC fitting procedure for the two-outcome model. Box plots show Gelman-Rubin statistics ($\\hat{R}$) for each of the variables in the model. Color indicates sample groups, which were fit using separate models. Values $\\hat{R} < 1.1$ are typically taken to represent satisfactory convergence. For variable definitions, see (\\ref{rating_m}) - (\\ref{nu_m}). \\label{2v_rhat}"}
library(tidyverse)
library(kableExtra)

load('../data/stan_postprocess_2v_t.rdata')

eff_prettied <- effects %>% mutate(variable=str_extract(variable, "\\w*(?=\\.|$)"))

plt <- ggplot(eff_prettied) + 
  geom_boxplot(aes(y=Rhat, x=variable, color=group)) +
  group_color_scale +
  labs(title="Convergence diagnostics:\nTwo-response model", size=rel(3)) +
  th + 
  theme(legend.position=c(0.78, 0.75))
plt
```

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.height=4, fig.width = 8, fig.cap="Convergence diagnostic for MCMC fitting procedure for the multi-outcome model. Box plots show Gelman-Rubin statistics ($\\hat{R}$) for each of the variables in the model. Color indicates sample groups, which were fit using separate models. Values $\\hat{R} < 1.1$ are typically taken to represent satisfactory convergence. For variable definitions, see (\\ref{rating_m}) - (\\ref{nu_m}). \\label{mv_rhat}"}
library(tidyverse)
library(kableExtra)

load('../data/stan_postprocess_mv_t.rdata')

eff_prettied <- effects %>% mutate(variable=str_extract(variable, "\\w*(?=\\.|$)"))

plt <- ggplot(eff_prettied) + 
  geom_boxplot(aes(y=Rhat, x=variable, color=group)) +
  group_color_scale +
  labs(title="Convergence diagnostics:\nAll-response model", size=rel(3)) +
  th + 
  theme(legend.position=c(0.7, 0.75))
plt
```


```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width=13, fig.height=4.5, fig.cap="Same as Figure 2, but for models with Student t distributions replaced by normal distributions.\\label{fig_2_norm}"}

source('../ggplot_setup.R')
load('../data/stan_postprocess_sv_norm.rdata')
effects <- effects %>% filter(group=='mturk')
dat <- dat %>% filter(group=='mturk')

############### Panel 1: Effect sizes for confidence ##################################
# get evidence effects
fe <- effects %>% filter(variable == 'mu', evidence != 'baseline') %>%
      select(mean, evidence, X2.5., X97.5.) %>%
      mutate(evidence=factor(evidence, levels=c("physicalDNA", 
                                                "physicalNon-DNA", 
                                                "witnessYes Witness", 
                                                "historyRelated", 
                                                "historyUnrelated")))

plt_1 <- ggplot(data=fe) +
  geom_pointrange(aes(x=evidence, y=mean, ymin=X2.5., ymax=X97.5.), color=color_conf, size=1.) + 
  evidence_x_axis +
  coord_cartesian(ylim=c(0,40)) +
  labs(title="A") +
  ylab("Confidence in Guilt (points)") +
  xlab("Evidence Effects") +
  geom_vline(xintercept=1.5, colour='grey') +
  geom_vline(xintercept=2.5, colour='grey') +
  geom_vline(xintercept=3.5, colour='grey') +
  geom_vline(xintercept=4.5, colour='grey') +
  th +
  theme(
    axis.text.x = element_text(hjust = 0.5, size=rel(1), color='black'))


############### Panel 2: Crime effects ##################################
# get scenario effects
se <- effects %>% filter(variable == 'gamma', evidence == 'baseline') %>% 
                  select(scenario, mean, group) %>%
                  mutate(outcome='rating')

plt_2 <- ggplot(data = se, aes(x=group, y=mean)) +
  geom_boxplot(aes(color=group), lwd=1, fatten=2.5, outlier.size=0, outlier.stroke=0) +
  geom_point(position=position_jitter(width=0.2), size=rel(4), aes(color=group), alpha=0.5) +
  group_x_axis +
  group_color_scale +
  group_fill_scale +
  xlab("Crime Effect") +
  coord_cartesian(ylim=c(0,40)) +
  labs(title="B", size=rel(3)) +
  ylab("Confidence") +
  th +
  theme(
    plot.margin=unit(c(5.5, 20, 5.5, 5.5), "points"),
    axis.line.y = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.title.y = element_blank(),
    axis.ticks.y = element_blank())

############### Panel 3: Illustration of range of confidences ##################################
# calculate mean rating for session and evidence combinations
sc_means <- dat %>% group_by(scenario, physical, history, witness) %>% 
                    summarise(rating=mean(rating)) %>%
                    arrange(scenario, physical, witness, history) %>%
                    ungroup()

# get unique variable code for each evidence combination
ev_codes <- sc_means %>% select(physical, witness, history) %>% 
                         distinct(physical, witness, history) %>%
                         mutate(code=as.factor(row_number()))

# add code column to scenario means
sc_means <- sc_means %>% merge(ev_codes) %>% arrange(code, scenario)

# calculate model prediction
# get mean values of coefficients across scenarios
betas <- effects %>% filter(variable == 'gamma') %>% 
         select(scenario, evidence, mean) %>%
         group_by(evidence) %>%
         summarise(effect=mean(mean)) %>%
         arrange(evidence)

# generate model matrix for predictions         
Xmat <- model.matrix(form, ev_codes)
colnames(Xmat)[1] <- 'baseline'
Xmat <- Xmat[, sort(colnames(Xmat), index.return=TRUE)$ix]

# remove baseline, calculate evidence
Xmat_no_baseline <- Xmat[,2:dim(Xmat)[2]]
betas_no_baseline <- betas %>% filter(evidence != 'baseline')

# mean evidence per scenario
pred_evidence <- data.frame(code=ev_codes$code, 
                            evidence=Xmat_no_baseline %*% betas_no_baseline$effect) %>%
                 merge(sc_means) 

# mean rating per scenario
mean_by_scenario <- dat %>% group_by(scenario) %>% 
                    summarise(sc_mean=mean(rating)) %>%
                    ungroup()

# prediction dataframe
pred_evidence <- pred_evidence %>% merge(mean_by_scenario)

plt_3 <- ggplot(data=pred_evidence) +
  geom_point(aes(x=evidence, y=rating, color=sc_mean), size=3, alpha=0.5) +
  geom_smooth(aes(x=evidence, y=rating), color=color_conf, method='lm', formula=y~x) +
  xlab("Weight of Model \nEvidence (points)") +
  coord_cartesian(xlim=c(-5, 70), ylim=c(0,100)) +
  labs(title="C", size=rel(3)) +
  ylab("Confidence in Guilt (observed)") +
  th

############### Combine into a single figure ##################################
# make a list of panels
plt_list <- list(plt_1, plt_2, plt_3)

# convert to grobs
grob_list <- lapply(plt_list, ggplotGrob)

# make sure axes align
max_heights <- do.call(unit.pmax, lapply(grob_list, function(x) {x$heights}))
grob_list <- lapply(grob_list, function(x) {x$heights <- max_heights; x})

# arrange with differing widths
plt_all <- do.call(arrangeGrob, c(grob_list, ncol=3, widths=list(c(1.1, 0.5, 1.25))))
grid.draw(plt_all)
```

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width=13, fig.height=10.5, fig.cap="Same as Figure 3, but for models with Student t distributions replaced by normal distributions.\\label{fig_3_norm}"}

source('../ggplot_setup.R')
load('../data/stan_postprocess_sv_norm.rdata')

############### Panel 1: Effect sizes for confidence ##################################
# get evidence effects
fe <- effects %>% filter(variable == 'mu', evidence != 'baseline') %>%
      select(mean, evidence, X2.5., X97.5., group) %>%
      mutate(evidence=factor(evidence, levels=c("physicalDNA", 
                                                "physicalNon-DNA", 
                                                "witnessYes Witness", 
                                                "historyRelated", 
                                                "historyUnrelated")))

plt_1 <- ggplot(data=fe) +
  geom_hline(yintercept=0, colour='grey') +
  geom_pointrange(aes(x=evidence, y=mean, ymin=X2.5., ymax=X97.5., color=group), size=1.,
                  position=position_dodge(width = 0.75)) + 
  evidence_x_axis +
  group_color_scale +
  coord_cartesian(ylim=c(-10,60)) +
  labs(title="A") +
  ylab("Confidence in Guilt (points)") +
  xlab("Evidence Effects") +
  geom_vline(xintercept=1.5, colour='grey') +
  geom_vline(xintercept=2.5, colour='grey') +
  geom_vline(xintercept=3.5, colour='grey') +
  geom_vline(xintercept=4.5, colour='grey') +
  th + 
  theme(
    axis.text.x = element_text(hjust = 0.5, size=rel(1), color='black')
  )

############### Panel 2: Baseline effects ##################################
# get scenario effects
se <- effects %>% filter(variable == 'gamma', evidence == 'baseline') %>% 
                  select(scenario, mean, group) %>%
                  mutate(outcome='rating')

plt_2 <- ggplot(data = se, aes(x=group, y=mean)) +
  geom_hline(yintercept=0, colour='grey') +
  geom_boxplot(aes(color=group), lwd=1, fatten=1, outlier.size=0, outlier.stroke=0) +
  # geom_point(position=position_jitter(width=0.2), size=rel(2), aes(color=group), alpha=0.5) +
  group_x_axis +
  group_color_scale +
  group_fill_scale +
  xlab("Crime Effect") +
  coord_cartesian(ylim=c(-10,60)) +
  labs(title="B", size=rel(3)) +
  ylab("Confidence") +
  th +
  theme(
    axis.line.y = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.title.y = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position=c(-0.5,1),
    legend.justification=c(0,1))
    

############### Panel 3: Illustration of range of confidences ##################################
# calculate mean rating for session and evidence combinations
sc_means <- dat %>% group_by(scenario, physical, history, witness, group) %>% 
                    summarise(rating=mean(rating)) %>%
                    arrange(scenario, physical, witness, history) %>%
                    ungroup()

# get unique variable code for each evidence combination
ev_codes <- sc_means %>% select(physical, witness, history) %>% 
                         distinct(physical, witness, history) %>%
                         mutate(code=as.factor(row_number()))

# add code column to scenario means
sc_means <- sc_means %>% merge(ev_codes) %>% arrange(code, scenario)

# calculate model prediction
# get mean values of coefficients across scenarios
betas <- effects %>% filter(variable == 'gamma') %>% 
         select(scenario, evidence, mean, group) %>%
         group_by(evidence, group) %>%
         summarise(effect=mean(mean)) %>%
         arrange(evidence)

# generate model matrix for predictions         
Xmat <- model.matrix(form, ev_codes)
colnames(Xmat)[1] <- 'baseline'
Xmat <- Xmat[, sort(colnames(Xmat), index.return=TRUE)$ix]

# remove baseline, calculate evidence
Xmat_no_baseline <- Xmat[,2:dim(Xmat)[2]]
betas_no_baseline <- betas %>% filter(evidence != 'baseline')

# mean evidence per code
pred_evidence <- betas_no_baseline %>% group_by(group) %>% 
                                       do(data.frame(code=ev_codes$code, 
                                             evidence=Xmat_no_baseline %*% .$effect)) 
# mean rating per code
mean_by_code <- dat %>% merge(ev_codes) %>% group_by(group, code) %>% 
                    summarise(code_mean=mean(rating)) %>%
                    ungroup()

# prediction dataframe
pred_evidence <- pred_evidence %>% merge(mean_by_code)

plt_3 <- ggplot(data=pred_evidence) +
  geom_point(aes(x=evidence, y=code_mean, color=group), size=3, alpha=0.5) +
  geom_smooth(aes(x=evidence, y=code_mean, color=group), method='lm', formula=y~x) +
  group_color_scale +
  xlab("Weight of Model \nEvidence (points)") +
  coord_cartesian(xlim=c(0, 85), ylim=c(0,100)) +
  labs(title="C", size=rel(3)) +
  ylab("Confidence in Guilt (observed)") +
  th 

############### Panel 4: Evidence vs Baseline #################################
eff_slopes <- effects %>% filter(variable=='gamma') %>%
  group_by(scenario, group) %>%
  filter(evidence != 'baseline') %>%
  summarise(slope=mean(mean))

eff_baselines <- effects %>% filter(variable=='gamma', evidence=='baseline') %>%
  select(-evidence) %>%
  group_by(scenario, group) %>%
  rename(baseline=mean) %>%
  select(baseline, scenario, group)

eff_slope_and_baseline <- merge(eff_baselines, eff_slopes)

plt_4 <- ggplot(data=eff_slope_and_baseline) +
  geom_smooth(aes(x=baseline, y=slope), method=lm, color="black", fill="black") +
  geom_point(aes(x=baseline, y=slope, color=group), size=4) + 
  group_color_scale +
  xlab('Crime') + ylab('Evidence') +
  labs(title="D", size=rel(3)) +
  th

############### Combine into a single figure ##################################
# make a list of panels
plt_list <- list(plt_1, plt_2, plt_3, plt_4)

# convert to grobs
grob_list <- lapply(plt_list, ggplotGrob)

# make sure axes align
max_heights <- do.call(unit.pmax, lapply(grob_list, function(x) {x$heights}))
grob_list <- lapply(grob_list, function(x) {x$heights <- max_heights; x})

# arrange with differing widths
lay <- rbind(c(1, 1, 2),
             c(3, 4, NA))
plt_all <- do.call(arrangeGrob, c(grob_list, ncol=3, layout_matrix=list(lay),
                                  widths=list(c(0.55, 0.55, 0.3))))
grid.draw(plt_all)
```

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width=13, fig.height=10.5, fig.cap="Same as Figure 4, but for models with Student t distributions replaced by normal distributions.\\label{fig_4_norm}"}
source('../ggplot_setup.R')
load('../data/stan_postprocess_mv_norm.rdata')

############### Panel 1: mTurk effects by outcome type ##################################
# get evidence effects
fe <- effects %>% filter(variable == 'mu', evidence != 'baseline') %>%
      select(mean, evidence, X2.5., X97.5., group, outcome) %>%
      mutate(evidence=factor(evidence, levels=c("physicalDNA", 
                                                "physicalNon-DNA", 
                                                "witnessYes Witness", 
                                                "historyRelated", 
                                                "historyUnrelated"))) %>%
      mutate(outcome=factor(outcome, levels=c("rating", 
                                              "rate_punishment", 
                                              "rate_outrage", 
                                              "rate_threat",
                                              "rate_threat_2"))) %>%
     filter(outcome != "rate_threat")

plt_1 <- ggplot(data=fe) +
  geom_hline(yintercept=0, colour='grey') +
  geom_pointrange(aes(x=evidence, y=mean, ymin=X2.5., ymax=X97.5., color=outcome), size=1.,
                  position=position_dodge(width = 0.75)) + 
  evidence_x_axis +
  outcome_color_scale +
  coord_cartesian(ylim=c(0,100)) +
  labs(title="A") +
  ylab("Effect Size (points)") +
  xlab("Evidence Effects") +
  geom_vline(xintercept=1.5, colour='grey') +
  geom_vline(xintercept=2.5, colour='grey') +
  geom_vline(xintercept=3.5, colour='grey') +
  geom_vline(xintercept=4.5, colour='grey') +
  th + 
  theme(
    axis.text.x = element_text(hjust = 0.5, size=rel(1), color='black')
  )


############### Panel 2: Baseline effects ##################################
# get scenario effects
se <- effects %>% filter(variable == 'gamma', evidence == 'baseline') %>% 
                  select(scenario, mean, group, outcome) %>%
      mutate(outcome=factor(outcome, levels=c("rating", 
                                              "rate_punishment", 
                                              "rate_outrage", 
                                              "rate_threat",
                                              "rate_threat_2"))) %>%
     filter(outcome != "rate_threat")

plt_2 <- ggplot(data = se, aes(x=outcome, y=mean)) +
  geom_hline(yintercept=0, colour='grey') +
  geom_boxplot(aes(color=outcome), lwd=1, fatten=1, outlier.size=0, outlier.stroke=0) +
  outcome_x_axis +
  outcome_color_scale +
  xlab("Crime Effect") +
  coord_cartesian(ylim=c(0,100)) +
  labs(title="B", size=rel(3)) +
  ylab("Confidence") +
  th +
  theme(
    axis.line.y = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.title.y = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position=c(-0.5,1),
    legend.justification=c(0,1))
    
############### Panel 3: Punishment and case strength effect correlations ##################################
outcomes <- levels(effects$outcome)
Nr <- length(outcomes)
releveler <- function(x) {
  # replace outcome numbers with names
  xfac <- factor(x, levels=1:length(outcomes), labels=outcomes)
  
  # now reorder levels so plot looks right
  factor(as.character(xfac), levels=c("rating", "rate_punishment", "rate_outrage", "rate_threat", "rate_threat_2"))
}
corrs <- effects %>% filter(grepl('Omega', variable)) %>% 
                     separate(variable, into=c("variable", "outcome1", "outcome2")) %>%
                     mutate_at(c("outcome1", "outcome2"), releveler) %>%
                     filter(evidence=='baseline') %>% 
                     filter(outcome1 != "rate_threat", outcome2 != "rate_threat") %>%
                     unite(col=contrast, outcome1, outcome2, sep='-') %>%
                     mutate(contrast=factor(contrast, levels=outcome_corr_levels,
                                                      labels=outcome_corr_labels))

plt_3 <- ggplot(data = corrs) +
  geom_hline(yintercept=0, colour='grey') +
  geom_pointrange(aes(x=contrast, y=X50., ymin=X2.5., ymax=X97.5.)) + 
  ylab('Crime Effect Correlation') +
  xlab('Outcome Pair') +
  labs(title="C", size=rel(3)) +
  coord_cartesian(ylim=c(-1,1)) +
  th +
  theme(
    axis.text.x = element_text(hjust = 0.5, size=rel(0.8), color='black')
    # axis.title.x = element_blank()
  )
  

############### Panel 4: Punishment and case strength effect correlations ##################################
load('../data/stan_postprocess_2v_norm.rdata')

plt_4 <- ggplot(data=(effects %>% filter(grepl('Omega', variable), evidence=='baseline'))) +
  geom_hline(yintercept=0, colour='grey') +
  geom_pointrange(aes(x=evidence, y=X50., ymin=X2.5., ymax=X97.5., color=group), 
                         position=position_dodge(width = 0.5)) + 
  xlab('Evidence') + ylab('\nConfidence in Guilt /\nPunishmnet Correlation') +
  group_color_scale +
  evidence_plus_baseline_x_axis +
  labs(title="D", size=rel(3)) +
  th + 
  theme(
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    plot.margin=unit(c(25.5, 100.5, 25.5, 0), "points"),
    legend.position=c(1.1, 0.8)
  )

############### Combine into a single figure ##################################
# make a list of panels
plt_list <- list(plt_1, plt_2, plt_3, plt_4)

# convert to grobs
grob_list <- lapply(plt_list, ggplotGrob)

# make sure axes align
max_heights <- do.call(unit.pmax, lapply(grob_list, function(x) {x$heights}))
grob_list <- lapply(grob_list, function(x) {x$heights <- max_heights; x})

# arrange with differing widths
lay <- rbind(c(1, 1, 2, NA),
             c(3, 3, 4, 4))
plt_all <- do.call(arrangeGrob, c(grob_list, ncol=4, layout_matrix=list(lay),
                                  widths=list(c(0.55, 0.55, 0.4, 0.4))))

grid.draw(plt_all)
```
\newpage

# Supplementary References